Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-09-10 introduction.tex
Typo

This paper represents the experience of how the ATLAS experiment has ``broken
free'' of the traditional computational approach of high-throughput computing
on distributed resources to embrace new platforms, in particular high-
performance computers (HPC). Specifically, we discuss the experience of
integrating PanDA WMS with a US DOE leadership machine (Titan) to reach
sustained production scales of approximately 51M core-hours a year.

>>>>

This paper represents the experience of how the ATLAS experiment has ``broken
free'' of the traditional computational approach of high-throughput computing
on distributed resources to embrace new platforms, in particular
high-performance computers (HPC). Specifically, we discuss the experience of
integrating PanDA WMS with a US DOE leadership machine (Titan) to reach
sustained production scales of approximately 51M core-hours a year.
